Assignment 3

### 2015-02-17 rmtw/a3/latex8.tex
Small changes
Changes to case study design

\Section{Purpose of the Study}
The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used. The study has been designed for change agents and it has been conducted at the EPG department at Ericsson. At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.

>>>>

\Section{Purpose of the Study}
The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used. The results of the study have been designed for change agents and it has been conducted at the EPG department at Ericsson. At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}. Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.
